### 2015-01-09 fundamentals/impl.tex
renaming section title to include 'Modular'
minor edits to todos
closes #50
compatibility with

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility heirarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the Cycamore library of
agents \TODO{archetypes?} and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

\subsection{Software Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'

@@

Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
performance on resource computing infrastructures. This limitation severely 
increases the wall-clock time necessary to conduct parameterized sensitivity 
analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
which are flexible and support parallelization. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \gls{HTC} systems.

>>>>

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility hierarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

\subsection{Modular Software Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'

@@

Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
performance on and compatibility with resource computing infrastructures. This limitation severely 
increases the wall-clock time necessary to conduct parameterized sensitivity 
analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
which are flexible and support parallelization. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \gls{HTC} systems.
